\problemname{James's Streets}

James has been invited to an incredibly important, exclusive conference at Moc-Yap that 
is sure to boost his career. Since James wouldn't miss this for the world,
he makes the 45 hour drive across the country to attend. 
In order to make it to the building where the conference is held,
he will have to cross the street and there are no designated 
sidewalks. This is a problem as James has a deathly 
fear of crossing streets without sidewalks. The only way he would ever possibly feel 
comfortable crossing the street is if he had at least $K$ seconds in which 
there was no car crossing as that is the fastest James can cross this street 
according to his calculations. Fortunately, even if a car reached James's
path at exactly the $Kth$ second from when James starts to cross the street, or if James
starts to cross the street right after a car crosses he will be safe. James plans to walk
in a straight line, perpendicular to the street to minimize his distance as well. James also considered
waiting until every car finished crossing before he started to cross the street, but there simply isn't enough
time to wait. If it's impossible to make it on time, he will have to let his manager know of his 
extenuating circumstances, but he needs to do so quickly.

\section*{Input}

The input consists of one test case. The input starts with a pair of integers, 
$N$ and $K$. $N$ is between $1$ and $100,000$ and $K$ is between $1$ and $50,000$. 
$N$ indicates the number of cars on the road and $K$ indicates the amount of 
time in seconds James requires to cross the street.
$N$ integers follow, $c_1, c_2, c_3, \dots c_N$, each between $-1,000,000$
and $1,000,000$, indicating the time, $|c_i|$, that car $c_i$ takes
to reach the path James is crossing. Each car has a negligible length in this scenario.
A negative time indicates a car coming from the left, and a positive 
number indicates a car coming from the right. If $c_i = c_j$ where $i \ne j$, 
$c_i$ and $c_j$ can be treated as one car.

\section*{Output}

Output the string "YES" if James can cross the street 
or "IMPOSSIBLE" if James cannot cross the street.